Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-08-25 manuscript/manuscript.tex
Changes in manuscript

We have developed a Python library that allows us to perform forward gravity computations using tesseroids with variable density in depth.
The code numerically approximates the integral that defines the gravity potential, its gradient and the Marussi tensor through the Gauss-Legendre Quadrature (GLQ).
It essentially consists in approximating the gravity fields of the tesseroids with the effect of point masses located on the scaled nodes of the Legendre polynomials.
We state that this method it's well suited to approximate the effect of tesseroids with arbitrary densities, in contrast with the ones that involve Taylor series expansion.

@@

On the other hand, there's no direct relation between the value of $D$ and the error of the computation, that's why we had to determine the minimum value of $D$ for each gravity magnitude that produces an acceptable accuracy.
These distance-size ratio determinations have been made through the comparison of the numerical approximation with the analytical solutions for the exceptional case of a spherical shell.
From the wide range of possible density variations, we've chosen a (1) linear, (2) an exponential and (3) a discontinuous density functions.

@@

On the other hand, the tests over the discontinuous function were not satisfactory.
In such cases we recommend to divide the model in several tesseroids, each one with a specific homogeneous density or a continuous density function, instead of using one variable density tesseroid.

>>>>

We have developed a Python library that allows us to perform forward gravity computations using tesseroids with variable density in depth.
The code numerically approximates the integral that defines the gravity potential, its gradient and the Marussi tensor through the Gauss-Legendre Quadrature (GLQ).
It essentially consists in approximating the gravity fields of the tesseroids with the effect of point masses located on the scaled nodes of the Legendre polynomials.
We have stated that this method it's well suited to approximate the effect of tesseroids with arbitrary densities, in contrast with the ones that involve Taylor series expansion.

@@

On the other hand, there's no direct relation between the value of $D$ and the error of the computation, that's why we had to determine the minimum value of $D$ that produces an acceptable accuracy for each gravity magnitude.
These distance-size ratio determinations have been made through the comparison of the numerical approximation with the analytical solutions for the exceptional case of a spherical shell.
From the wide range of possible density variations, we've chosen a linear, an exponential and a discontinuous density functions.

@@

On the other hand, the tests over the discontinuous function were not satisfactory.
In such cases we recommend to divide the model in several tesseroids, each one with a specific homogeneous density or a continuous density function, instead of using a single variable density tesseroid.
